Analysis of PDX Growth Data

### 2022-03-02 proposal_presentation.Rmd
presentation update

---
title: "Proposal Presentation"
author: "Peyton Kuhlers"
date: "3/2/2022"
output: 
  beamer_presentation:
    theme: "AnnArbor"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Background

@@

@@

@@

## Proposal

@@

- My proposal is to used a mixed model approach to analyze the PDXNet growth data

@@

## Model

>>>>

---
title: "Analysis of PDX Growth Data"
author: "Peyton Kuhlers"
date: "3/2/2022"
output: 
  beamer_presentation:
    theme: "AnnArbor"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background

@@

- Becoming preferred model as they preserve donor genomic characteristics
and allow for microenvironment modelling *in vivo*

@@

\note{In contrast to cells in a dish}

@@

## Significance

@@

@@

## Analysis

- Mixed effects model of tumor growth

\centering
$E[Y_{i}|b_i] = \beta_0 + b_{i1} + \beta_1(time_{i}) + b_{i2}(time) + \gamma_i (agent_i*time)$

## Result Reporting

- Profile Plots (shown above)

- Forest plot of interaction coefficients

- Table of specific pairwise contrasts between different therapies

- Variance of random effects

- As a secondary analysis, test methods from Evrard et al 
at e.g. day 75 and compare to model contrasts at day 75.

##

Thank You! Questions?
